Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-27 paper.qmd
typo in python code block

```{=tex}
# functions/functions.py
Py> def train_and_predict_output(simulated_df: pd.DataFrame) -> pd.DataFrame:
+     # ... scientific logic ...
+     return format_results(predictions)
end{CodeInput}
```

>>>>

```{=tex}
\begin{CodeInput}
# functions/functions.py
Py> def train_and_predict_output(simulated_df: pd.DataFrame) -> pd.DataFrame:
+     # ... scientific logic ...
+     return format_results(predictions)
\end{CodeInput}
```
